Post-Disturbance Tree Community Trajectories in a Neotropical Forest

### 2018-04-19 WholePlotTrajectories.Rmd
Figures

The taxonomic diversity was assessed through Richness and the Hill number translation of Shannon and Simpson indices [@Hill1973]. 
To tackle the unequal number of recruited trees among treatments the indices bias corrected estimator were used, following [@Chao2015;@Marcon2015b].
These three indices belong to the set of HCDT or generalized entropy, respectively corresponding to the 0, 1 and 2 order of diversity (q), which proved well suited for diversity studies [@Patil1982;@Tothmeresz1995]. 
The functional diversity was reported using the Rao index of quadratic entropy which combines species abundance distribution and average pairwise dissimilarity based on all functional and life traits.

@@

```{r Fig5, out.width = '100%', fig.asp = 1.5/3, echo=FALSE,fig.cap="Trajectories of the difference to reference inventory over 30 years after disturbance of plots communities **(a)** Richness, **(b)** Shannon and **(c)** Simpson diversities. Trajectories correspond to the median (solid line) and 0.025 and 0.975 percentile (gray envelope) observed after 50 iteration of the taxonomic uncertainty propagation. Initial treatments are represented by solid lines colorswith green for control, blue for T1,orange for T2 and red for T3.", fig.env="figure*"}
load("DB/ReplacementTraj_ForGraphs")

@@

While for undisturbed plots the Richness, Shannon and Simpson diversity remained comparable to the values in 1989, the trajectories of all disturbed plots showed significant increase positively correlated with the disturbance intensity (Figure \@ref(fig:Fig5)). 
The Richness was less affected by the initial disturbance except for the higher intensity (T3 plots) (Figure \@ref(fig:Fig5)). 
The Shannon and Simpson diversities however first significantly increased, illustrating an increasing evenness, before reaching a maximum around 15 years after disturbance for all plots except one from T1 treatment and one from T2 treatment (Figure \@ref(fig:Fig5)).

>>>>

The taxonomic diversity was assessed through Richness and the Hill number translation of Shannon and Simpson indices [@Hill1973]. 
>>To tackle the unequal number of recruited trees among treatments the indices bias corrected estimator were used, following [@Chao2015;@Marcon2015b].

These three indices belong to the set of HCDT or generalized entropy, respectively corresponding to the 0, 1 and 2 order of diversity (q), which proved well suited for diversity studies [@Patil1982;@Tothmeresz1995]. 
The functional diversity was reported using the Rao index of quadratic entropy which combines species abundance distribution and average pairwise dissimilarity based on all functional and life traits.

@@

```{r Fig5, out.width = '100%', fig.asp = 1.5/3, echo=FALSE,fig.cap="Trajectories of the difference to the 1989 inventories (5 years after disturbance) over 30 years after disturbance of plots communities **(a)** Richness, **(b)** Shannon and **(c)** Simpson diversities. Trajectories correspond to the median (solid line) and 0.025 and 0.975 percentile (gray envelope) observed after 50 iteration of the taxonomic uncertainty propagation. Initial treatments are represented by solid lines colors with green for control, blue for T1,orange for T2 and red for T3.", fig.env="figure*"}
load("DB/ReplacementTraj_ForGraphs")

@@

While for undisturbed plots the Richness, Shannon and Simpson diversity remained comparable to the values in 1989, the trajectories of all disturbed plots showed significant increase positively correlated with the disturbance intensity ($\rho_{spearman}^{Shannon}=0.87$, and $\rho_{spearman}^{Simpson}=0.88$) (Figure \@ref(fig:Fig5)). 
The Richness was less affected by the initial disturbance except for the higher intensity (T3 plots) (Figure \@ref(fig:Fig5)). 
The Shannon and Simpson diversities however first significantly increased, illustrating an increasing evenness, before reaching a maximum around 15 years after disturbance for all plots except one from T1 treatment and one from T2 treatment (Figure \@ref(fig:Fig5)).

### 2018-04-19 WholePlotTrajectories.tex
Figures

The taxonomic diversity was assessed through Richness and the Hill
number translation of Shannon and Simpson indices \citep{Hill1973}. To
tackle the unequal number of recruited trees among treatments the
indices bias corrected estimator were used, following
\citep{Chao2015, Marcon2015b}. These three indices belong to the set of
HCDT or generalized entropy, respectively corresponding to the 0, 1 and
2 order of diversity (q), which proved well suited for diversity studies
\citep{Patil1982, Tothmeresz1995}. The functional diversity was reported
using the Rao index of quadratic entropy which combines species
abundance distribution and average pairwise dissimilarity based on all
functional and life traits.

@@

\caption{Trajectories of the difference to reference inventory over 30 years after disturbance of plots communities **(a)** Richness, **(b)** Shannon and **(c)** Simpson diversities. Trajectories correspond to the median (solid line) and 0.025 and 0.975 percentile (gray envelope) observed after 50 iteration of the taxonomic uncertainty propagation. Initial treatments are represented by solid lines colorswith green for control, blue for T1,orange for T2 and red for T3.}\label{fig:Fig5}
\end{figure*}

While for undisturbed plots the Richness, Shannon and Simpson diversity
remained comparable to the values in 1989, the trajectories of all
disturbed plots showed significant increase positively correlated with
the disturbance intensity (Figure \ref{fig:Fig5}). The Richness was less
affected by the initial disturbance except for the higher intensity (T3
plots) (Figure \ref{fig:Fig5}). The Shannon and Simpson diversities
however first significantly increased, illustrating an increasing
evenness, before reaching a maximum around 15 years after disturbance
for all plots except one from T1 treatment and one from T2 treatment
(Figure \ref{fig:Fig5}).

>>>>

The taxonomic diversity was assessed through Richness and the Hill
number translation of Shannon and Simpson indices \citep{Hill1973}.
\textgreater{}\textgreater{}To tackle the unequal number of recruited
trees among treatments the indices bias corrected estimator were used,
following \citep{Chao2015, Marcon2015b}.

These three indices belong to the set of HCDT or generalized entropy,
respectively corresponding to the 0, 1 and 2 order of diversity (q),
which proved well suited for diversity studies
\citep{Patil1982, Tothmeresz1995}. The functional diversity was reported
using the Rao index of quadratic entropy which combines species
abundance distribution and average pairwise dissimilarity based on all
functional and life traits.

@@

\caption{Trajectories of the difference to the 1989 inventories (5 years after disturbance) over 30 years after disturbance of plots communities **(a)** Richness, **(b)** Shannon and **(c)** Simpson diversities. Trajectories correspond to the median (solid line) and 0.025 and 0.975 percentile (gray envelope) observed after 50 iteration of the taxonomic uncertainty propagation. Initial treatments are represented by solid lines colors with green for control, blue for T1,orange for T2 and red for T3.}\label{fig:Fig5}
\end{figure*}

While for undisturbed plots the Richness, Shannon and Simpson diversity
remained comparable to the values in 1989, the trajectories of all
disturbed plots showed significant increase positively correlated with
the disturbance intensity (\(\rho_{spearman}^{Shannon}=0.87\), and
\(\rho_{spearman}^{Simpson}=0.88\)) (Figure \ref{fig:Fig5}). The
Richness was less affected by the initial disturbance except for the
higher intensity (T3 plots) (Figure \ref{fig:Fig5}). The Shannon and
Simpson diversities however first significantly increased, illustrating
an increasing evenness, before reaching a maximum around 15 years after
disturbance for all plots except one from T1 treatment and one from T2
treatment (Figure \ref{fig:Fig5}).
